Bird beak's elaboration and exploration: data preparation

### 2022-08-04 Analysis/01-Data_preparation.Rmd
Update 01-Data_preparation.Rmd

```{r load_beer, eval = TRUE}
## Loading packages
library(dispRity) #v>=1.7
```

@@

```{r}
## Temporary change the empty levels to noclade
clades <- clades_list[, c(1)]
levels(clades)[1] <- "noclade"

@@

```{r, echo = FALSE}
kable(summary(shape_axes)[, c(1:((length(shape_axes$dimensions)+1)*2))], caption = "variance per axes for the Shape space", label = "Table X2")
```

>>>>

```{r load_beer, eval = TRUE}
## Loading packages
library(dispRity) #v>=1.7
library(xtable)
library(knitr)
source("../Functions/stats.utilities.R")

```

@@

```{r}
## Temporary change the empty levels to noclade
clades <- clades_list[, c(1)]
levels(clades)[1] <- "no clade"

@@

```{r, echo = FALSE}
kable(summary(shape_axes)[, c(1:((length(shape_axes$dimensions)+1)*2))], caption = "variance per axes for the Shape space", label = "Table X2")
to_export <- summary(shape_axes)[, c(1:((length(shape_axes$dimensions)+1)*2))]
rownames(to_export)[nrow(to_export)] <- "Entire space"
silent <- make.xtable(to_export, caption = "Variance per axis and per group in the shape space. The \"no clade\" group contains birds not attributed to any of the other groups (i.e. from a clade with less than 15 species).", label = "tab_variance_per_axis", path = "../Manuscript/Tables/", include.rownames = TRUE)
```
